### 2019-04-11 Thesis/games.tex
new.

    \item If $\sigma \from \oc\V_\Gamma \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\V_\Gamma \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
      \[
        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
        \]
      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, where $M=\lambda x.M'$, then
      \begin{align*}
        \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
        \plot_X^\Gamma \neww_X M\,.
      \end{align*}
  \end{itemize}
\end{definition}

@@

  Lastly, suppose that $\Gamma,s\ts M,N\from S \to T$ and suppose that $\Gamma,s\ts M \opto \Gamma,s\ts N$.
  Let $\sigma\from \oc\V_\Gamma \implies (\oc\deno S \implies \deno T)$ be a strategy and suppose that $\sigma \plot_{S\to T} N$.  
  We claim that $\sigma \plot_{S\to T} M$.  
  Indeed, let $\tau\from\oc\V_\Gamma\implies\deno S$ be a strategy and let $\Gamma \ts P\from S$ be a term in context such that $\tau\plot_S^\Gamma P$.  
  Then, since $\sigma\plot_{S\to T} N$, we must have that $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev \plot_T^\Gamma N\,P$.  
  Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.

  In the case that $S=\Var$ and $T=X$ is a datatype, we also need to show that $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev\plot_X^\Gamma\neww_X(\lambda x.M\,x)$.  
  Writing $\sigma'$ for the composite $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev$, we know already that $\sigma'\plot_X^\Gamma \neww_X(\lambda x.N\,x)$.
  Let $s$ be a $\Gamma$-store.  
  Then we know that if $\seqdeno{s,\sigma'}\ne\bot_{\oc\V_\Gamma\implies X}$, then $\seqdeno{s,\sigma'}=\seqdeno{s',u}$ for some $s'$, $u$ such that $\Gamma,\neww_X \lambda x.N\,x\converges u,s'$.
  It follows that $\Gamma,x,(s\vert x\mapsto 0)\ts N\,x\converges u,s'$; then, since $\Gamma,x,(s\vert x\mapsto 0)\ts M\,x\opto \Gamma,x(s\vert_x\mapsto 0)\ts N\,x$, we have $\Gamma,x\ts M\,x\converges u,s'$ by Lemma \ref{LemSoundnessOpto}.
  Therefore, $\Gamma,s\ts \neww_X \lambda x.M\,x \ts u,s'$.  
  Since $s$ was arbitrary, it follows that $\sigma'\plot_X^\Gamma \new_X(\lambda x.M\,x)$.
\end{proof}

@@

  We are required to show that
  \[
    \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\bot\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
    \]
  which, by induction, we can do by showing that it is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
  Indeed, we may write this composite as
  \[
    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\oc\V_\Gamma \tensor \tau^\dag} \oc\V_\Gamma\tensor\oc\deno S \xrightarrow{\Lambda\inv(\bot_{\oc\V_\Gamma \implies (\oc\deno S \implies \deno T))}} \deno T\,,
    \]
  which is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.

  Lastly, in the special case that $S=\Var$ and $T=X$ is a datatype, we need to show that
  \begin{align*}
    \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
    \plot_X^\Gamma \neww_X M\,.
  \end{align*}
  Indeed, this composite is equal to $\bot_{\oc\V_\Gamma\implies X}$ by an identical argument.
\end{proof}

@@

    \item Now we move on to the conditional.  
      Suppose that we have $\Gamma,\Delta\ts M\from \nat$ and $\Gamma,\Delta\ts N,P\from X$ for some datatype $X$.  
      Let $s$ be a $\Gamma$-store.  
      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\oc\V_\Gamma\ts \bN}$, then
      \[
        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{\oc\V_\Gamma \ts X}\,.
        \]
      Otherwise, by induction we know that $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}}=\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$ such that $\Gamma,s\ts M[N_i/x_i]\converges n,s'$.
      Without loss of generality, suppose that $n=0$.  
      Then we have
      \begin{IEEEeqnarray*}{Cl}
        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma\,\Delta\ts \IfO M \Then N \Else P})} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO 0 \Then N \Else P})} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta \ts N})}\,. \\
      \end{IEEEeqnarray*}
      Then, by induction, this last term is either equal to $\bot_{X\sequoid\V_\Gamma}$,or is equal to $\seqdeno{\Gamma,s''\ts u}$ for some $u\in X$ such that $\Gamma,s'\ts N[N_i/x_i]\converges u,s''$.
      In this second case, we have $\Gamma,s\ts \IfO M[N_i/x_i] \Then N[N_i/x_i] \Else P[N_i/x_i] \converges u,s''$.
  \end{itemize}
  Next, we deal with the rules for variables.
  \begin{itemize}
    \item Suppose $\Gamma,\Delta\ts V\from\Var$, and suppose we already know that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var} V[N_i/x_i]\,.
        \]
      Then by definition we have
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \oc V} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_{\bN} \plot_{\bN}^\Gamma \oc\V[N_i/x_i]\,.
        \]
      Suppose $\Gamma,\Delta\ts E\from \nat$, and suppose we know already that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E} \plot_{\bN} E[N_i/x_i]$.  
      Then, for all $s$, either $\seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E}}=\bot_{\bN \sequoid\oc\V_\Gamma}$ -- in which case
      \[
        \seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets E}} = \bot_{\bC \sequoid \oc\V_\Gamma}
        \]
      (since $\assign$ is a strict strategy) -- or it is equal to $\seqdeno{s',n}$ for some $n\in \bN$ such that $\Gamma,s\ts E[N_i/x_i]\converges n,s'$.
      In the second case, we have
      \begin{IEEEeqnarray*}{Cl}
        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V \gets E})} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets n}} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)} \\
        \plot_{\Var}^\Gamma & V[N_i/x_i]\gets n\,.
      \end{IEEEeqnarray*}
      Then, since we have $\Gamma,s,V[N_i/x_i]\gets E[N_i/x_i] \opto \cdots \opto \Gamma,s',V[N_i/x_i]\gets n$, the claim follows by Lemma \ref{LemAdequacyOpto}.
    \item Suppose that $\Gamma,\Delta\ts W \from \nat \to \com$ and that $\Gamma,\Delta \ts R \from \nat$.
      We claim that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts\mkvar\,W\,R};\pr_n\plot_\com^\Gamma (\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\gets n$ for each $n$ and that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN\plot_\nat^\Gamma \oc(\mkvar\,W[N_i/x_i]\,R[N_i/x_i])$.

>>>>

    \item If $\sigma \from \oc\V_\Gamma \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\V_\Gamma \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
      \[
        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,.
        \]
  \end{itemize}
\end{definition}

@@

  Lastly, suppose that $\Gamma,s\ts M,N\from S \to T$ and suppose that $\Gamma,s\ts M \opto \Gamma,s\ts N$.
  Let $\sigma\from \oc\V_\Gamma \implies (\oc\deno S \implies \deno T)$ be a strategy and suppose that $\sigma \plot_{S\to T} N$.  
  We claim that $\sigma \plot_{S\to T} M$.  
  Indeed, let $\tau\from\oc\V_\Gamma\implies\deno S$ be a strategy and let $\Gamma \ts P\from S$ be a term in context such that $\tau\plot_S^\Gamma P$.  
  Then, since $\sigma\plot_{S\to T} N$, we must have that $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev \plot_T^\Gamma N\,P$.  
  Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.
\end{proof}

@@

  We are required to show that
  \[
    \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\bot\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
    \]
  which, by induction, we can do by showing that it is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
  Indeed, we may write this composite as
  \[
    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\oc\V_\Gamma \tensor \tau^\dag} \oc\V_\Gamma\tensor\oc\deno S \xrightarrow{\Lambda\inv(\bot_{\oc\V_\Gamma \implies (\oc\deno S \implies \deno T))}} \deno T\,,
    \]
  which is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
\end{proof}

@@

    \item Now we move on to the conditional.  
      Suppose that we have $\Gamma,\Delta\ts M\from \nat$ and $\Gamma,\Delta\ts N,P\from X$ for some datatype $X$.  
      Let $s$ be a $\Gamma$-store.  
      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\oc\V_\Gamma\ts \bN}$, then
      \[
        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{\oc\V_\Gamma \ts X}\,.
        \]
      Otherwise, by induction we know that $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}}=\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$ such that $\Gamma,s\ts M[N_i/x_i]\converges n,s'$.
      Without loss of generality, suppose that $n=0$.  
      Then we have
      \begin{IEEEeqnarray*}{Cl}
        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma\,\Delta\ts \IfO M \Then N \Else P})} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO 0 \Then N \Else P})} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta \ts N})}\,. \\
      \end{IEEEeqnarray*}
      Then, by induction, this last term is either equal to $\bot_{X\sequoid\V_\Gamma}$,or is equal to $\seqdeno{\Gamma,s''\ts u}$ for some $u\in X$ such that $\Gamma,s'\ts N[N_i/x_i]\converges u,s''$.
      In this second case, we have $\Gamma,s\ts \IfO M[N_i/x_i] \Then N[N_i/x_i] \Else P[N_i/x_i] \converges u,s''$.
  \end{itemize}
  Next, we deal with the rules for variables.
  \begin{itemize}
    \item Suppose $\Gamma,\Delta\ts V\from\Var$, and suppose we already know that
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var}^\Gamma V[N_i/x_i]\,.
        \]
      Then by definition we have
      \[
        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \oc V} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_{\bN} \plot_{\bN}^\Gamma \oc\V[N_i/x_i]\,.
        \]
      Suppose $\Gamma,\Delta\ts E\from \nat$, and suppose we know already that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E} \plot_{\bN} E[N_i/x_i]$.  
      Then, for all $s$, either $\seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E}}=\bot_{\bN \sequoid\oc\V_\Gamma}$ -- in which case
      \[
        \seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets E}} = \bot_{\bC \sequoid \oc\V_\Gamma}
        \]
      (since $\assign$ is a strict strategy) -- or it is equal to $\seqdeno{s',n}$ for some $n\in \bN$ such that $\Gamma,s\ts E[N_i/x_i]\converges n,s'$.
      In the second case, we have
      \begin{IEEEeqnarray*}{Cl}
        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V \gets E})} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets n}} \\
        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)}\,.
      \end{IEEEeqnarray*}
      Now we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n\plot_{\Var}^\Gamma V[N_i/x_i]$ by induction, so this composite is either equal to 
      Then, since we have $\Gamma,s,V[N_i/x_i]\gets E[N_i/x_i] \opto \cdots \opto \Gamma,s',V[N_i/x_i]\gets n$, the claim follows by Lemma \ref{LemAdequacyOpto}.
    \item Suppose that $\Gamma,\Delta\ts W \from \nat \to \com$ and that $\Gamma,\Delta \ts R \from \nat$.
      We claim that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts\mkvar\,W\,R};\pr_n\plot_\com^\Gamma (\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\gets n$ for each $n$ and that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN\plot_\nat^\Gamma \oc(\mkvar\,W[N_i/x_i]\,R[N_i/x_i])$.
